---
#name: Sourav
surname: Sourav Sarker
# position: "Software Engineer"
# address: "[Secure Link Services Ltd, Dhaka, Bangladesh (SELISE)(https://selisegroup.com/)]"
# address: "225/12 B, Pallabi, Mirpur-12, Dhaka-1216"
email: "sourav39.dev@gmail.com"
www: iamsourav.ml
linkedin: sourav-sarker-6a9029b8
location: Dhaka, Bangladesh
github: po95
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv
linkcolor: red
urlcolor: red
citecolor: red
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

<!-- \normalsize -->
<!-- As a Bioinformatician with a strong background in biochemistry and molecular biology, I have expanded my expertise in computational biology by integrating advanced NGS technologies like Illumina and Nanopore. My work is driven by a commitment to leveraging computational and biological advances to explore the complexities of life. -->

\footnotesize
\vspace{.2mm} 

Having a colorful footprint in software engineering spanning over four years, I have cultivated a robust skill set that includes clean coding, system design, settling R&Ds and debugging abilities; also, my commitment to problem-solving is demonstrated through successful project completions. Now, I am fueled by an unwavering passion for delving into challenging research topic which makes me an ideal candidate for contributing in.

# Education
\footnotesize
\vspace{-2mm} 
```{r education2}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Shahjalal University of Science and Technology(SUST)", "Bachelor of Science in Biochemistry and Molecular Biology", "2016-2019", "Sylhet, Bangladesh",
    list(
      paste0("CGPA: 3.36 out of 4.00\\\\",
             "\\hspace*{-0.28cm}•\\,\\, Project (2019): Prediction of Missing DNA Methylation from Whole Genome Bisulfite Data Using KNN\\\\",
             "\\hspace*{0.020cm}∙ Advisor: Rashedul Islam - PhD in Bioinformatics - University of British Columbia, Canada")
    ),
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```
\vspace{2mm} 
# Research Experiences
\footnotesize
\vspace{-2.4mm} 

```{r professional_experience}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ responsibilities,
  "Research Officer, Bioinformatician - Genomics Team ", "Child Health Research Foundation", "Dhaka, Bangladesh", "01 Aug 2022 - Present",
    list(
      paste0("CZI A Global Pediatric Cell Atlas of Nasal and Oral Mucosa.\\\\",
             "\\hspace*{0.5cm}- Single cell isolation, Single cell capture, Whole transcriptomic amplification, Library preparation using HoneyComb, 10x Genomics, Parse Biosciences and loading on NextSeq2000.\\\\",
             "\\hspace*{0.5cm}- Computational analysis using Scanpy and Seurat.\\\\",
             "\\hspace*{0.020cm}∙ Training: From the team members of Ordovas-Montanes Lab, Assistant Professor Harvard Medical School.\\\\",
             "\\hspace*{0.020cm}∙ Workshop: Attented 2024 HCA Single‐Cell Omics in‐person Computational and Experimental Design Workshop, Bangkok, Thailand\\\\",
             "\\hspace*{0.020cm}∙ Collaboration: Ordovas-Montañes Lab - Boston Childrens Hospital, MIT\\\\",
             "\\hspace*{-0.28cm}•\\,\\, A computational framework to automatically interpret pediatric chest X-rays and diagnose pneumonia.\\\\",
             "\\hspace*{0.5cm}- Model development using CNN and Pytorch.\\\\",
             "\\hspace*{0.020cm}∙ Funded by: NIHR Global Health Research Unit on Respiratory Health\\\\",
             
             "\\hspace*{-0.28cm}•\\,\\, Parv4 detection in children with suspected meningitis is associated with high mortality.\\\\",
             "\\hspace*{0.5cm}- Metagenomics analysis—consensus sequence generated using CZ ID, mapping, MAFFT, RAxML, and annotation.\\\\",
             "\\hspace*{-0.28cm}•\\,\\, Global Pneumococcal Sequencing Project.\\\\",
             "\\hspace*{0.5cm}- Development of Nextflow workflow.\\\\",
             "\\hspace*{0.020cm}∙ Advanced Bioinformatics Workshop developed for GPS and JUNO projects by Wellcome Sanger Institute in Bangalore, India.\\\\",
             "\\hspace*{-0.28cm}•\\,\\, RSV Vaccine Impact Monte Carlo Simulation.\\\\",
             "\\hspace*{0.5cm}- RSV vaccination mortality impact analysis via Monte Carlo simulation.\\\\",
             "\\hspace*{0.020cm}∙ PI: Sudipta Saha - Harvard University")
    ),
  "Research Fellow", "National Gene Bank, National Institute of Biotechnology(NIB)", "Dhaka, Bangladesh", "5 Sept 2021 - 30 June 2022",
    list(
      paste0("Revealing the Disease complexity and Population Structure of Human Gut Microbiota from Diverse Cohort of Bangladesh Population.\\\\",
             "\\hspace*{0.5cm}- Metagenomic analysis of 16s rRNA sequences using qiime2.")
    ),
)%>% 
  detailed_entries(role, dates, organization, loc, responsibilities)

```



# Teaching Experience 
\footnotesize
\vspace{-3mm} 

```{r teaching}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ details,
  "Teaching Assistant, Building Scientists for Bangladesh", "Child Health Research Foundation (CHRF)", "Dhaka, Bangladesh", "2023-2024",
  
    list(
      paste0("Advanced Next Generation Sequencing\\\\", 
             # "\\hspace*{0.020cm}∙ Topics Covered:\\\\",
             "\\hspace*{0.5cm}- Linux OS, NGS Data Analysis: Quality checking, Quality filter, Genome Assembly, Genome Annotation\\\\", 
             "\\hspace*{0.5cm}- Building Consensus using CZID, Sample Sheet Preparation for NextSeq2000\\\\",
             "\\hspace*{-0.28cm}•\\,\\, Bacterial Genomics Antimicrobial Resistance\\\\", 
             # "\\hspace*{0.020cm}∙ Topics Covered:\\\\",
             "\\hspace*{0.5cm}- Linux OS, Bash Scripting Genome Assembly, Genome Mapping, Genome Annotation, Genome Submission, MLST Prediction\\\\",
             "\\hspace*{-0.28cm}•\\,\\, AI in Public Health\\\\",
             # "\\hspace*{0.020cm}∙ Topics Covered:\\\\", 
             "\\hspace*{0.5cm}- Data cleaning and preprocessing, Data Visualization, Architecture of ML and DL Libraries- Numpy,Pandas, Keras,TensorFlow\\\\",
             "\\hspace*{0.5cm}- Dengue prediction in Puerto Rico using LSTM and ARIMA\\\\",
             "\\hspace*{0.5cm}- Predicting Pneumonia in X-rays using CNN\\\\",
             "\\hspace*{0.5cm}- Advanced Modeling Techniques- PyCaret, GRU\\\\",
             "\\hspace*{0.020cm}∙ Supported from the Bill and Melinda Gates foundation, through the Democratizing Public Health Modeling Using AI-based Tools")
    ),
  "Instructor, Bioinformatics Division", "Bioinformatics Division, National Institute of Biotechnology (NIB)", "Dhaka, Bangladesh", "2021",
    list(
      paste0("Delivered training on Bioinformatics for Biotechnology Research\\\\",
             # "\\hspace*{0.020cm}∙ Topics covered:\\\\",
             "\\hspace*{0.5cm}- Linux OS, Bash Scripting and Biopython for NGS Data Analysis")
    ),
) %>%
  detailed_entries(role, dates, organization, loc, details)
```



# Technical Skills
\footnotesize
\vspace{-4mm} 
- **Languages:** Bash, Python, C, R, Nextflow, Java
- **Database Management Systems:** SQL, Redis, SQLite3
<!-- - **Web Development:** Quarto®,Django -->
- **Machine Learning and Deep Learning:** Proficient in various frameworks and techniques: Numpy, Pandas, Matplotlib, Seaborn, Keras, SciKit-Learn, TensorFlow, PyTorch
- **Bioinformatics:** 
  - Proficient in Docker for pipeline buildup.
  - Microarray and Bulk RNA sequencing Analysis using DESeq2, stats, ggplot, corrplot, pheatmap, EDASeq, gProfileR
  - Genome quality checking and assembly: **Illumina:-** BCL2fastq, fastQC, MultiQC, Quast, Trimmomatic, fastp, Unicycler, Spades, Megahit; **Nanopore:-** fast52fasta, Pilon, Flye
  - Genome annotation: Kraken2 , Prokka, Seroba, AMRFinderPlus, Abricat, SRST, MLST, Snippy, Mafft, fasta2phylip, Raxml-ng, Poppunk, PlasmidFinder, ResFinder
  - Molecular Dynamics Simulation using GROMACS.
  - Metagenomics analysis using qiime2 and CZID.
  - Nextstrain Built and maintained from Bangladesh for SARS-CoV-2.
  - **Single Cell RNA sequencing Analysis using Scanpy and Seurat: Data pre-processing, Clustering and Cell annotation, Integration and Batch correction, Cell-cell communication, BCR background and 10x analysis, Trajectory inference, Differential abundance, Multiomic scATAC**
  
- **Wet Lab:** 
  - Single Cell RNA sequencing Analysis using  HoneyComb, 10x Genomics, Parse
Biosciences, Library preparation, Sequence on Illumina and Nanopore
  - Molecular techniques: Conventional and Real-time PCR, DNA & RNA extraction, Agarose & Polyacrylamide Gel Electrophoresis and Imaging, Blotting techniques, Molecular cloning, ELISA & ICT
  - Microbiological techniques: Culture, Biochemical test



# Publications
\footnotesize
\vspace{-2.4mm} 

**Dev,P.,C.,** Rehman,A., Hossain,M.,M., Kazi,E., Goswami,S., Rehman,H., Hooda,Y., Tanmoy,A.,M., Saha,S.,K., Saha, S. **Genomic epidemiology of Salmonella Paratyphi B isolates from Bangladesh**.**(In-process)**

\vspace{-1.3mm} 
Debnath, J., P., Hossen,K., Khandaker,M., S., Sayed,S., B., **Dev, P., C.,*** Sarker, S.,* Hossain,T.* Influenza and Other Respiratory Viruses. **Decoding the Unique Gene Signatures Upon 2022 MPXV Infection: Predictive Biomarkers and Drug Targets via Transcriptomic Network Analysis and Machine Learning Models.****(Submitted)**

\vspace{-1.3mm} 
Islam,S., Kabiraj,R., Sarkar,H., **Dev,P.,C.,** Akter,A.T., Purna,D.K., Rajib,A.M., Mohammad,A.T., Kumar,S.S., Hooda,Y., Saha,S. Microbiology Resource Announcements: **Genome sequences of bacteriophages that infect Salmonella Typhi from Bangladesh.(Submitted)** 

\vspace{-1.3mm} 
Raju,R.,.S., Nahid,A.,A., **Dev,P.,C.,** Islam,R. **VirusTaxo: Taxonomic classification of viruses from the genome sequence using k-mer enrichment.** Genomics. 2022 Jul;114(4):110414. doi: 10.1016/j.ygeno.2022.110414. Epub 2022 Jun 17. PMID: 35718090.

\vspace{-1.3mm} 
Chowdhury,Z.,M., Bhattacharjee,A., Ahammad,I., Hossain,M.,U., Jaber,A.A., Rahman,A., **Dev,P.,C.,** Salimullah,M., Keya,C.,A. **Exploration of Streptococcus core genome to reveal druggable targets and novel therapeutics against S. pneumoniae.** PLoS One. 2022 Aug 18;17(8):e0272945. doi: 10.1371/journal.pone.0272945. PMID: 35980906; PMCID: PMC9387852.

<!-- \vspace{-1.3mm}  -->
<!-- Hasnat,M.,A., Niloy,F.,R., Ashik,A.,I., Hassan,M., **Dev,P.,C.,**, Panna,S.,S., Mia,M.,W., Hasan, Z. **Prevalence of hyperlipidemia in controlled and uncontrolled type-2 diabetic patients.** Journal of Advanced Biotechnology and Experimental Therapeutics. 2022 Jan; 5(1):247. doi: 10.5455/jabet.2022.d112 -->

 
 

# Conference  Presentations
\footnotesize
\vspace{-2.4mm} 
**Dev,P.,C.,*** Malaker, A.,R., Keya,D.,P., Hooda,Y., Saha,S., **Building a single-cell atlas of the nasopharyngeal mucosa to investigate SARS-CoV-2 infection**. 2024 HCA Single-Cell Omics in-person Computational and Experimental Design Workshop, Bangkok, Thailand. 

\vspace{-1.3mm} 
**Dev,P.,C.,*** Tanmoy,A.,M., Rahman,A., Saha,S.,K., Hooda,Y., Saha,S., **Paratype v1.1: recent updates to the genotyping tool for paratyphoid fever surveillance**. 13th International Conference on Typhoid and Other Invasive Salmonelloses, Kigali, Rwanda.

<!-- \vspace{-1.3mm}  -->
<!-- Rehman,A., **Dev,P.,C.,***, Hossain,M.,M., Kazi,E., Goswami,S., Rehman,H., Hooda,Y., Tanmoy,A.,M., Saha,S.,K., Saha, S. **Genomic epidemiology of Salmonella Paratyphi B isolates from Bangladesh**. 13th International Conference on Typhoid and Other Invasive Salmonelloses, Kigali, Rwanda. -->

<!-- Chowdhury ZM, Bhattacharjee A, Ahammad I, Hossain MU, Jaber AA, Rahman A, **Chondrow Dev P**, Salimullah M, Keya CA. **Exploration of Streptococcus core genome to reveal druggable targets and novel therapeutics against S. pneumoniae**. Presented at the 2nd International Conference on Genomics, Nanotech, and Bioengineering-2022 (ICGNB-2022), North South University, Dhaka. -->




             
<!-- # Project -->
<!-- For a complete list of projects see my  [**Github**](https://github.com/preonath) \faGithub -->
<!-- ```{r project}  -->
<!-- tribble( -->
<!--   ~ role, ~ project_name, ~ loc, ~ dates, ~ details, -->

<!--    "Computational analyst and AI model developer", "A Global Pediatric Cell Atlas of Nasal and Oral Mucosa", "CHRF, Dhaka, Bangladesh", "Present", -->
<!--    list("Collaboration: Ordovas-Montañes Lab - Boston Childrens Hospital, MIT, Bill and Melinda Gates Foundation"), -->

<!--    "AI Developer", "Paediatric pneumonia detection from X-ray images using deep learning", "CHRF, Dhaka, Bangladesh", "Present", -->
<!--    list("Funded by: NIHR Global Health Research Unit on Respiratory Health"), -->

<!--    "Bioinformatics analysis and development of pipeline", "Exploring diversity and environmental dynamics of Salmonella Typhi and its bacteriophages", "CHRF, Dhaka, Bangladesh", "Present", -->
<!--    list("Collaboration: Stanford University School Medicine"), -->

<!--    "AI Developer", "Predicting Disease Spread of Dengue using LSTM", "CHRF, Dhaka, Bangladesh", "Present", -->
<!--    list("Competitions: DrivenData"), -->

<!--    "Model Developer", "RSV Vaccine Impact Monte Carlo Simulation", "CHRF, Dhaka, Bangladesh", "Present", -->
<!--    list("Collaboration: Sudipta Saha (PhD Student) - Population Health Sciences, Harvard University"), -->
<!--    "Bioinformatics analysis and development of AI pipeline", -->
<!--    "Prediction of Missing DNA Methylation fromWhole Genome Bisulfite Data Using KNN","Dhaka, Bangladesh","2019", -->
<!--    list("Collaboration: Rashedul Islam - PhD in Bioinformatics - University of British Columbia, Canada") -->

<!--  ) %>% -->
<!--    detailed_entries(role, dates, project_name, loc, details) -->


<!-- ```  -->


<!-- # Courses -->
<!-- For my courses and workshops visit my personal [**website**.](https://preonath.github.io/) -->

<!-- ```{r workshops} -->
<!-- tribble( -->
<!--   ~ role, ~ course, ~ organisation, ~ country, ~ dates, ~ details, -->
<!--   "Participant", "Introduction to Deep Learning in Python", "Datacamp", "Online", "AUG 04, 2021", "Participated in an online course focusing on the basics of deep learning using Python.", -->
<!--   "Participant", "Introduction to R", "Datacamp", "Online", "JUL 27, 2021", "Completed an introductory course on the R programming language, covering fundamental concepts and applications." -->
<!-- ) %>% -->
<!--   brief_entries(glue::glue("\\textbf{<course>}: <role> (<organisation>, <country>)  \\newline <details>", .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE) -->

<!-- ``` -->

<!-- # Seminar -->

<!-- ```{r seminar} -->
<!-- tribble( -->
<!--   ~ role, ~ organizer, ~ loc, ~ dates, ~ details, -->
<!-- "Participant", "Human Cell Atlas and Wellcome Sanger Institute", "Virtual ", "2022-2024", -->
<!--    list("\\vspace{1mm}HCA ASIA 2023 MEETING", -->
<!--         "Focus on Technology: Advances in Spatial Omics", -->
<!--         "Atlas Integration and CAP (Cell Annotation Platform)", -->
<!--         "GPS and JUNO seminar"), -->
<!-- ) %>% -->
<!--   detailed_entries(role, dates, organizer, loc, details) -->

<!-- ``` -->


# Accomplishment
\footnotesize
\vspace{.2mm} 
```{r accomplishment}
tribble(
  ~ award,  ~ organisation, ~ country, ~ dates, ~ details,
  "6th Position from Bangladesh", "Rosalind", "SUST", "2018-2024", "Bioinformatics problem solving using Python.\\vspace{1.25mm}",
  
   "100+ Problem solved", "Leetcode",  "SUST","2022-2023", "Problem solving in competitive programming using Python.\\vspace{1.25mm}",
  
  "220 out of 13558", "DrivenData", "CHRFBD Datascience Team - Dhaka, Bangladesh", "2023-2024", "Predicting Disease Spread of Dengue using LSTM.\\vspace{1.25mm}",
  
  "Thesis Supervision", "Child Health Research Foundation (CHRF)", "Dhaka, Bangladesh", "2022-2024", "Assist \\textbf{4 students and 1 intern} with executing the bioinformatics pipeline for their projects.\\vspace{1.25mm}",
  
    "Academic Honor", " Dept. of Biochemistry and Molecular Biology(SUST)", "Sylhet, Bangladesh", "2016-2019", "Merit-based scholarship for academic excellence in the 1st and 4th year.\\vspace{1.25mm}"
  
  
) %>% 
brief_entries(glue::glue("\\textbf{<award>}: <organisation>, <country>  \\newline <details>", .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE)
```

# References
\footnotesize
\vspace{-2mm} 

```{r reference}
tribble(
  ~ role, ~ organizer, ~ loc, ~ dates, ~ details,
"Assistant Professor, Dept. of Biochemistry and Molecular Biology", "Tanvir Hossain", "Sylhet, Bangladesh", "SUST",  
    list(
      paste0("\\hspace*{-0.37cm} PhD Candidate, Australian Institute for Bioengineering and Nanotechnology\\\\",
             "\\hspace*{-0.37cm} The University of Queensland, Brisbane, Australia\\\\",
             "\\hspace*{-0.37cm} Email: tanvir-bmb@sust.edu")
    ),
  # "Associate Professor, Dept. of Biochemistry and Molecular Biology", "Ajit Ghosh,PhD", "Sylhet, Bangladesh", "SUST", 
  #   list(
  #     paste0("\\hspace*{-0.37cm} Email: aghosh-bmb@sust.edu")
  #   ),

"Senior Scientific Officer, Bioinformatics Division", "Mohammad Uzzal Hossain", "Dhaka, Bangladesh", "National Institute of Biotechnology(NIB)", 
    list(
      paste0("\\hspace*{-0.37cm} MSc, Oxford University\\\\",
             "\\hspace*{-0.37cm} Email: uzzal.nib.edu")
    ),
  
"Scientist", "Dr Yogesh Hooda", "Dhaka, Bangladesh", "CHRF",
    list(
      paste0("\\hspace*{-0.37cm} Post-doc, MRC lab-Cambridge University\\\\",
             # "\\hspace*{-0.37cm} PhD, University of Torrento, Canada\\\\",
             "\\hspace*{-0.37cm} Email: yhooda@chrfbd.org")
    )
)%>% 
  detailed_entries(role, dates, organizer, loc, details)

```
<!-- # Problem Solving  -->

<!-- ```{r problem} -->
<!-- tribble( -->
<!--   ~ host,  ~ url,  ~ dates, ~ details, -->
<!--   "Rosalind", "https://rosalind.info/users/Preonath/",  "June 2018 - Present", "6th Position from Bangladesh" -->
<!--   "HackerRank", "https://www.hackerrank.com/profile/preonath2838",  "2018", "Total Hackos: 357", -->

<!--   "CodingBat", "https://codingbat.com/python",  "April 2020", "Count:53", -->

<!--   "Leetcode", "https://leetcode.com/Preonath/",  "2022 - Present", "Rank 1761864", -->
<!-- ) %>%  -->
<!--   brief_entries(glue::glue("\\textbf{{\\href{{<url>}}{{<host>}}}}: \\newline <details>", .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE) -->


<!-- ``` -->




<!-- # Volunteering Experience -->

<!-- ```{r volunteering} -->
<!--  tribble( -->
<!--    ~ role, ~ organization, ~ loc, ~ dates, ~ details, -->

<!--     # "Academic Team Member", "Bangladesh Mathematical Olympiad", "Dhaka, Bangladesh", "2018-2021", -->
<!--     #  list("Engaged in evaluating examination papers and overseeing exam hall activities to ensure a smooth conduct of the Olympiad" -->
<!--     #       ), -->
<!-- # "Academic Team Member", "Bangladesh Physics Olympiad", "Dhaka, Bangladesh", "2021", -->
<!-- #      list("Tasked with the assessment of solutions and maintaining order among candidates during the Olympiad competitions" -->
<!-- #     ), -->

<!-- # "Academic Team Member", "Bangladesh Olympiad on Astronomy and Astrophysics", "Dhaka, Bangladesh", "2021", -->
<!-- #      list("Played a crucial role in monitoring examination procedures and providing assistance to participants throughout the event." -->
<!-- #     ), -->
<!--      "ENZYME", "Bangladesh Biology Olympiad ", "Dhaka, Bangladesh", "2021", -->
<!--      list("Assisted in the evaluation process and managed the exam hall logistics to facilitate a fair and efficient Olympiad" -->
<!--     ), -->
<!--     #  "General Executive Member", "Copernicus Astronomical Memorial of SUST", "Dhaka, Bangladesh", "2021", -->
<!--     #  list("Participated in and directed several outreach programs aimed at educating the public about astronomy and piqueing students' interest in the subject.", -->
<!--     #  "Facilitated a better understanding and enjoyment of astronomy by organizing and judging competitions in which students presented projects they had worked on." -->
<!--     # ), -->
<!-- #     "General Member", "SUST Science Arena", "Dhaka, Bangladesh", "2021", -->
<!-- #      list("Organize conferences, seminers, science fairs, quiz competitions, science weeks, social activities" -->
<!-- #     ), -->
<!-- "Mentor", "Bioinformatics School", "Dhaka, Bangladesh", "2021", -->
<!--      list("Solve the different kinds of bioinformatics related problem of the group members" -->
<!--     ), -->
<!-- ) %>% -->
<!--   detailed_entries(role, dates, organization, loc, details) -->
<!-- ``` -->




