---
# name: Sourav
surname: Sourav Sarker
# position: "Software Engineer"
address: "\\tiny Dhaka, Bangladesh"
email: "sourav39.dev@gmail.com"
www: iamsourav.site
# phone: "+880-1765-651957"
linkedin: sourav-sarker-6a9029b8
mylocation: Bangladesh
github: sarker39
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv
linkcolor: red
urlcolor: red
citecolor: red
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```
# Objective
\footnotesize
\vspace{.2mm} 
Having a colorful footprint in software engineering spanning over six years, I have cultivated a robust
skill set that includes clean coding, system design, settling R&Ds and debugging abilities; also, my
commitment to problem-solving is demonstrated through successful project completions. Now, I am
fueled by an unwavering passion for delving into challenging research topic which makes me an ideal
candidate for contributing in research.


# Education
\footnotesize
\vspace{-2mm} 
```{r education2}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Bachelor of Science in Computer Science & Engineering", "Shahjalal University of Science & Technology", "Sylhet, Bangladesh", "Mar 2015 — Feb 2019",
    list(
      paste0("{\\textbf{CGPA: 3.28 / 4.00}}\\\\")
    )
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```
# Work Experience
\footnotesize
\scriptsize
\vspace{-2mm}

```{r work_experience}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ details,
  
  "Software Engineer (Team Lead)", "SELISE Digital Platform", "Dhaka, Bangladesh", "Apr 2020 — Present",
    list(
      paste0("{\\textbf{Acting as a team lead:}}\\\\",
             "\\hspace*{0.5cm}- Led an engineering team of 4 in developing a Fintech software, generating close to CHF 1 million annually for the company.\\\\", 
             "\\hspace*{0.5cm}- Worked within a tech team on a Swiss platform for insurance, pension, and broker sectors, enabling secure communication and data exchange.\\\\", 
             "\\hspace*{0.5cm}- Contributed to the platform's plans to expand into a community-driven marketplace for third-party services and industry digitalization.\\\\", 
             "\\hspace*{-0.28cm}•\\,\\, 
             {\\textbf{Acting as a full-stack dev:}}\\\\",
             "\\hspace*{0.5cm}- Working on a scalable application designed to manage complete financial activities, assets, and plans for Swiss citizens."),
            "\\vspace{1mm}"
    ),
  
  "Junior Software Engineer", "Secure Link Services Ltd.", "Dhaka, Bangladesh", "Apr 2019 — Mar 2020",
    list(
      paste0("\\hspace*{0.5cm}- Worked on a report generation tool that optimized the yearly business process for shareholders.\\\\",
             "\\hspace*{0.5cm}- Worked on a report generation tool that optimized the yearly business process for shareholders.\\\\", 
             "\\hspace*{0.5cm}- Developed a project management system similar to Trello, using MongoDB, Node.js, and Socket.io.")
    )
) %>%
  detailed_entries(role, dates, organization, loc, details)

```
\vspace{4mm}
# Research Experience
\scriptsize
\vspace{-2.4mm}

```{r research_experience}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ responsibilities,
  
  "Research Assistant", 
  "Department of Computer Science & Engineering, SUST", 
  "Sylhet, Bangladesh", 
  "Jan 2018 - Feb 2019",
    list(
  "\\begingroup\\leftskip=6mm Collaborated with a team of researchers on a project focused on building a factoid question answering system in Bengali.",
  "Collected and preprocessed datasets from various sources, ensuring data quality and integrity.",
  "Implemented and fine-tuned NLP models using open-source machine learning libraries.",
  "Conducted literature reviews to identify relevant research, contributing insights to project strategy.",
  "Assisted in designing and conducting experiments, analyzing results, and presenting findings during weekly team meetings.",
  "Presented research progress at a regional NLP conference via poster presentation and published two papers.",
  "\\endgroup \\vspace{2mm}"
    ),
  
  "Executive Member", 
  "SUST Natural Language Processing Lab", 
  "Sylhet, Bangladesh", 
  "July 2018 - June 2019",
    list(
      "\\begingroup\\leftskip=6mm Collaborated with a multidisciplinary team to build a Named Entity Recognition (NER) model for the Bengali search engine 'Pipilika'.",
      "Assisted in experimental design, conducted empirical evaluations, and analyzed results to refine model performance.",
      "Participated in workshops and seminars arranged by the SUST NLP Lab to stay updated with advancements in NLP and machine learning.","\\endgroup"
      
    )
) %>% 
  detailed_entries(role, dates, organization, loc, responsibilities)
```

# Publications
\vspace{-2.4mm} 

- Sarker, S., **"Bengali Question Answering System for Factoid Questions: A statistical approach,"** \textit{2019 2nd International Conference on Bangla Speech and Language Processing (ICBSLP)}, Sylhet, Bangladesh, 2019, pp. 1-5. \href{https://doi.org/10.1109/ICBSLP47725.2019.201512}{\textbf{doi: 10.1109/ICBSLP47725.2019.201512}}.

- Sarker, S., **"Classification of Bengali Questions Towards a Factoid Question Answering System,"** \textit{2019 1st International Conference on Advances in Science, Engineering and Robotics Technology (ICASERT)}, Dhaka, Bangladesh, 2019, pp. 1-5. \href{https://doi.org/10.1109/ICASERT.2019.8934567}{\textbf{doi: 10.1109/ICASERT.2019.8934567}}.

# Technical Skills
\footnotesize
\scriptsize
\vspace{-4mm} 

- **Languages:** C, C#, Python, JavaScript, MATLAB
- **Frameworks:** Dotnet, Angular
- **Database Management Systems:** SQL, NoSQL, Redis
- **Data Analysis & Machine Learning:** Proficient in various frameworks and techniques: Numpy, Pandas, Matplotlib, Keras, SciKit-Learn, TensorFlow
- **Tools:** Git, Jupyter Notebook, Visual Studio, Visual Studio Code, MS Office
- **Web Development:** Full stack development experience, including project management
- **Project Management:** Experience leading engineering teams and utilizing Agile methodologies in software development



# Achievements

\footnotesize
\vspace{.2mm} 
\scriptsize
```{r accomplishment}
library(dplyr)
library(tibble)
library(glue)

tribble(
  ~ award,  ~ organisation, ~ country, ~ dates, ~ details,
  
  "\\textbf{\\textit{Best Poster Award}}", 
    "International Conference on Bangla Speech and Language Processing (ICBSLP-2018)", 
    "Sylhet, Bangladesh", 
    "2018", 
    "Awarded in the poster presentation segment. \\vspace{1.25mm}",
  
  "\\textbf{\\textit{Runner-up}} (Twice)", 
    "Bangladesh Mathematical Olympiad (BdMO) - Secondary Level",  
    "Bangladesh", 
    "2010 \\newline 2012", 
    "Secured runner-up position twice in the regional phase. \\vspace{1.25mm}",
  
  "\\textbf{\\textit{Champion}}", 
    "National Earth Olympiad (NEO) arranged by BYEI", 
    "Bangladesh", 
    "2013", 
    "Achieved the champion title in the National Earth Olympiad.\\vspace{1.25mm}"
  
) %>% 
  brief_entries(
    glue::glue("<award>: <organisation>, <country> \\newline <details>", .open = "<", .close = ">"), 
    paste0(dates, "\\newline"), 
    .protect = FALSE
  )
```


# Test Scores

\footnotesize
\vspace{-4mm} 
- **IELTS:** Overall Band 6.5 (No band less than 6.0)

# Language
\footnotesize
\vspace{-4mm} 
- English (Fluent) - Bengali (Native) - Hindi (Intermediate)



